Performance comparison of Dask and Apache Spark on HPC systems

### 2022-02-22 latex/paper.tex
[UPDATE] write about I/O bottleneck limitations.

\section{Discussion}
\subsection{I/O bottleneck}
We used Lustre as shared file system as it is a \HL{de facto} solution in HPC systems.
The performance of our Lustre installation degrades when a large number of concurrent tasks attempt to perform I/O to the shared file system, as shown in Figures \ref{fig:increment_worker} and \ref{fig:histogram_worker}.
In a previous study~\cite{8943502}, we observed nearly no improvement when increasing the number of nodes to process an application while using an NFS.
In this paper, Lustre shows some scaling when increasing the number of nodes, although not linear.
This suggests that increasing the parallelism level of the file system, including through potential configuration optimizations, might help alleviate the I/O bottleneck observed.

As in our previous study~\cite{8943502}, we observe that the I/O bottleneck from the file system has a lower impact on more compute-intensive applications, such as BIDS App Example.
However, it significantly affects data-intensive applications, such as Increment and Histogram.

These results suggest that increasing the parallelism of the file system is critical when scaling the compute resources to process a data-intensive application.
Otherwise, the compute resource might be underutilized.
% TODO talk about the limitation of our current setup.

@@

\section*{Acknowledgment}
Mathieu Dugre\'e was funded by an Alexander Graham Bell scholarship from
the Natural Sciences and Engineering Research Council of Canada. This work
was partially funded by the Canada Research Chairs program. The HPC cluster
was funded by the Canada Foundation for Innovation.

>>>>

\section{Discussion}
\subsection{I/O bottleneck}
We used Lustre as shared file system as it is a \HL{de facto} solution in HPC systems.
The performance of our Lustre installation degrades when a large number of concurrent tasks attempt to perform I/O to the shared file system, as shown in Figures \ref{fig:increment_worker} and \ref{fig:histogram_worker}.
In a previous study~\cite{8943502}, we observed nearly no improvement when increasing the number of nodes to process an application while using an NFS.
\HL{In this paper, the performance scale when increasing the number of nodes, although not linear due to an I/O bottleneck.
	The system was designed such that the filesystem has similar speed to the network.
	Upgrading to more performant networking and storage compononents would reduce the bottleneck seen when increasing the number of workers.

	As in our previous study~{\cite{8943502}}, we observe that the I/O bottleneck has a lower impact on more compute-intensive applications, such as Kmeans and BIDS App Example.
	However, it significantly affects data-intensive applications, such as Increment and Histogram.
}

These results suggest that increasing the parallelism of the file system \HL{and speed of the network} is critical when scaling the compute resources to process a data-intensive application.
Otherwise, the compute resource might be underutilized.

@@

\section*{Acknowledgment}
Mathieu Dugr\'e was funded by an Alexander Graham Bell scholarship from
the Natural Sciences and Engineering Research Council of Canada. This work
was partially funded by the Canada Research Chairs program. The HPC cluster
was funded by the Canada Foundation for Innovation.
